---
title: "Sweave/Knitr for reproducible research with LaTeX"
author: "Juan R Gonzalez"

output:
  BiocStyle::pdf_document:
    toc_depth: 2
  BiocStyle::html_document:
    toc_depth: 2
---

<!-- to compile this:
library("rmarkdown");
render("rr-auhtoring.Rmd", output_format="all")
or just call make
-->

```{r style, echo=FALSE, message=FALSE, warning=FALSE, results="asis"}
library("knitr")
#options(width=100)
opts_chunk$set(message = FALSE, error = TRUE, warning = TRUE)
```




# Reproducible research (RR)

- In it's most general sense... the ability to reproduce results from an experiment or analysis conducted by another.

- From Wikipedia... `The ultimate product is the **paper along with the full computational environment** used to produce the results in the paper such as the code, data, etc. that can be **used to reproduce the results and create new work** based on the research

- Concept is strongly based on the idea of **literate programming** such that the logic of the analysis is clearly represented in the final product by combining computer code/programs with ordinary human language [Knuth, 1992].

## Example of non-reproducible research
1. Gather data
 - Begins with general question or research objectives
 - Data collected in raw format (hard copy) converted to digital (Excel spreadsheet)
2. Analyze data
 - Import data into stats program or analyze directly in Excel
 - Create figures/tables directly in stats program
 -  Save relevant output
3. Report Result
 - Create research report using Word or other software
 - Manually insert results into report
 - Change final report by hand if methods/analysis altered

## Example of reproducible research
1. Gather data
 - Begins with general question or research objectives
 - Data collected in raw format (hard copy) converted to digital **text file**
2. Analyze data 
 - Create **integrated script** for importing data (data path is known)
 - Create figures/tables directly in stats program
 - **No need to export** (reproduced on the fly)
3. Report Result
 - Create research report using RR software
 - **Automatically include results** into report
 - **Change final report automatically** if methods/analysis altered

Easily adopted using [RStudio](http://www.rstudio.com/). Also possible with [Tinn-R](https://sourceforge.net/projects/tinn-r/) or via command prompt but not as intuitive.
Requires a LaTeX distribution system - use [MikTex for Windows](http://miktex.org/). It is essentially a
LaTeX document that incorporates R code and these programs use Sweave (or Knitr) to convert .Rnw file 
to .tex file, then LaTeX is used to create pdf files. Sweave comes with `utils` package, Knitr should be 
loaded. 

# References

# Session information

```{r, echo=FALSE}
sessionInfo()
```

 
